---
title: "Analysis_Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis_Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction

In this document, we will demonstrate how to use the **Survey-Embedded Carbon Footprint Calculator (SECFC)** package. We will:

1. Install the SECFC package from GitHub.
2. Load SECFC and our sample dataset.
3. Calculate carbon emissions using a built-in SECFC function.
4. Run a linear regression to see how *income* predicts total carbon emissions.
5. Create a plot of the data using **ggplot2**.


## Step 1: Download the package from GitHub

First, we need to install the package from GitHub. If you do not have `remotes` installed yet, run `install.packages("remotes")` beforehand.

```{r warning=FALSE, message=FALSE,eval=T}
# Install the SECFC package from GitHub
remotes::install_github("jianing-d/SECFC")
```

```{r warning=FALSE, message=FALSE}
library(SECFC)
```

## Step 2: Load the package
Load the SECFC package, which provides the ```calc_total_emissions()``` function among others.

## Step 3: Load your dataset
For demonstration, we assume you are use questionnaire_sample.rds that contains survey responses (provided and pre-loaded in our package). 

```{r warning=FALSE, message=FALSE}
# Replace the file path with your own dataset if necessary
questionnaire_example <- SECFC::questionnaire_example

# Take a quick look at your data structure
str(questionnaire_example)
```

## Step 4: Calculate total carbon emissions
Now we use the ```calc_total_emissions()``` function from SECFC to estimate each respondent’s carbon footprint based on their survey responses. The returned data frame will include a new column called TotalEmissions.

```{r warning=FALSE, message=FALSE}
carbon_total <- calc_total_emissions(questionnaire_example)

# Check the first few rows
head(carbon_total)
```

## Step 5: Run a linear regression
We will examine how a respondent’s income might predict their total carbon emissions. This is a basic linear model using the built-in ```lm()``` function.

```{r warning=FALSE, message=FALSE}
model <- lm(TotalEmissions ~ income, data = carbon_total)

# Display summary statistics of the regression
summary(model)
```

## Step 6: Create a Plot
Finally, we can visualize the relationship between income and TotalEmissions using ```ggplot2```. The plot below includes:

- Points representing individual respondents
- A linear regression line (and confidence interval)

```{r warning=FALSE, message=FALSE}
# Load ggplot2
library(ggplot2)

# Define custom colors
point_color <- "#4A6D8C"  # desaturated blue-grey for points
line_color  <- "#2C3E50"  # deeper blue-grey for the regression line

lm_plot <- ggplot(carbon_total, aes(x = income, y = TotalEmissions)) +
  geom_point(color = point_color, size = 2.8, alpha = 0.8) +
  geom_smooth(method = "lm", se = TRUE, color = line_color, linewidth = 1.2) +
  labs(
    title = "Income and Total Carbon Emissions",
    x = "Annual Income (USD)",
    y = "Total Emissions (kg CO2e)"
  ) +
  theme_classic(base_size = 14) +
  theme(
    plot.title   = element_text(face = "bold", hjust = 0.5, color = line_color),
    axis.title   = element_text(color = line_color),
    axis.text    = element_text(color = "black"),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.8),
    plot.margin  = margin(10, 10, 10, 10)
  )

# Print the plot
lm_plot
```
