---
title: "Get Started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Getting Started

Install the package

```{r echo=FALSE}
#install.packages("remotes")
remotes::install_github("jianing-d/SECFC")
```

## How to Use SECFC

Follow these steps to calculate survey-based carbon footprints using SECFC.

### Step 1: Load the Package
After installation, load the package with:
```{r}
library(SECFC)
```

### Step 2: Import Your Survey Dataset
Make sure your dataset is in a data frame or tibble format. If you're using the Qualtrics template we provided, ensure that variable names match exactly.
Here is an example of the expected data structure:
```{r}
library(tibble)

data <- tribble(
  ~StartDate, ~EndDate, ~Status, ~IPAddress, ~Progress, ~`Duration (in seconds)`, ~Finished, ~RecordedDate, ~ResponseId,
  ~RecipientLastName, ~RecipientFirstName, ~RecipientEmail, ~ExternalReference, ~LocationLatitude, ~LocationLongitude,
  ~DistributionChannel, ~UserLanguage, ~Q39, ~CL_01_ClothingPurcha, ~CL_03_MonthlyEx_9, ~CL_03_MonthlyEx_10, ~CL_03_MonthlyEx_11,
  ~CL_03_MonthlyEx_12, ~CL_03_MonthlyEx_13, ~CL_03_MonthlyEx_14, ~CL_03_MonthlyEx_15, ~F_01_DietaryHabits_5,
  ~F_01_DietaryHabits_6, ~F_01_DietaryHabits_7, ~F_01_DietaryHabits_4, ~T_01_CarUsage, ~T_02_CarType, ~T_03_CarDistance,
  ~T_04_PublicTransport, ~T_05_PublicTransport, ~T_06_AirTravelLong, ~T_07_AirTravelShort, ~T_08_LongDistanceTra,
  ~EH_02_ElectricityBil_1, ~EH_03_ElectricityBil_1, ~EH_05_NaturalGasBill_1, ~EH_06_NaturalGasBill_1, ~PETS_4, ~PETS_5,
  ~SD_06_HouseholdSize_17, ~SD_06_HouseholdSize_18, ~SD_06_HouseholdSize_19, ~SD_07_Country, ~SD_08_ZipCode,
  
  "3/20/25 9:43", "3/20/25 9:47", "IP Address", "111.187.123.25", 100, 240, TRUE, "3/20/25 9:47", "R_3lENNCNKNsOdbgd",
  NA, NA, NA, NA, 31.2222, 121.4581, "anonymous", "EN", "Yes, I accept to proceed to the study",
  "7-12 times (About every 1-2 months)", 30, 250, 50, 0, 50, 100, 200, 7, 3, 4, 6, "5-6 days",
  "Gasoline Vehicle", "11-50 km or 6.2-31 miles", "Weekly", "5-10 km or 3.1-6.2 miles", "1-3 flights",
  "1-3 flights", "Monthly", 120, 1440, 50, 600, 1, 1, 2, 1, 0, "United States", 10001
)
```

âœ… Note
The following columns are automatically generated when you export responses from Qualtrics:
~StartDate, ~EndDate, ~Status, ~IPAddress, ~Progress, ~`Duration (in seconds)`, ~Finished, ~RecordedDate, ~ResponseId,  
~RecipientLastName, ~RecipientFirstName, ~RecipientEmail, ~ExternalReference, ~LocationLatitude, ~LocationLongitude,  
~DistributionChannel, ~UserLanguage

### Step 3: Run Emission Calculations
Now you're ready to calculate emissions. Choose the functions depending on whether you want only the calculation results or also the process data.

#### ðŸ›’Consumption Emissions 
Calculate the carbon footprint from general consumption.
```{r}
cons <- calc_cons_emissions(data)
```
With process details:
```{r}
cons_process <- calc_cons_emissions_process(data)
```
#### ðŸ½ Food Emissions ï¸
Calculate the carbon footprint from food consumption.
```{r}
food <- calc_food_emissions(data)
```
With process details:
```{r}
food_process <- calc_food_emissions_process(data)
```
#### ðŸ  Housing Emissions 
Calculate the carbon footprint from housing energy use.
```{r}
housing <- calc_housing_emissions(data)
```
With process details:
```{r}
housing_process <- calc_housing_emissions_process(data)
```
#### ðŸ¶ Pet Emissions 
Calculate the carbon footprint from pet ownership.
```{r}
pet <- calc_pet_emissions(data)
```
With process details:
```{r}
pet_process <- calc_pet_emissions_process(data)
```
#### ðŸš— Transport Emissions 
Calculate the carbon footprint from daily and long-distance transportation.
```{r}
transport <- calc_transport_emissions(data)
```
With process details:
```{r}
transport_process <- calc_transport_emissions_process(data)
```
#### ðŸŒ Total Emissions 
Calculate the total carbon footprint across all domains.
```{r}
total <- calc_total_emissions(data)
```
With process details:
```{r}
total_process <- calc_total_emissions_process(data)
```


âœ… Note
The following columns are automatically generated when you export responses from Qualtrics:
~StartDate, ~EndDate, ~Status, ~IPAddress, ~Progress, ~`Duration (in seconds)`, ~Finished, ~RecordedDate, ~ResponseId,  
~RecipientLastName, ~RecipientFirstName, ~RecipientEmail, ~ExternalReference, ~LocationLatitude, ~LocationLongitude,  
~DistributionChannel, ~UserLanguage
